\tool

### 2018-04-03 paper/paper.tex
Reading group 4/3

Our evaluation was limited to Java projects since \textsc{Error Prone} only analyzes Java code. \tool~requires Maven, a build automation and dependency management system for Java projects, to run tools by automatically modifying the Project Object Model (\textit{pom.xml}) configuration file and building projects.  Our approach targets projects that don't use \textsc{Error Prone} to increase awareness for developers who are not already knowledgeable about the tool. We chose the most starred repositories to study the most popular projects on GitHub.Stars are a social aspect of GitHub where users can indicate favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}.

To get the most popular repositories, we filtered GitHub projects by separating them based on the amount of stars between numbers in the Fibonnaci sequence. This allowed us to get a higher concentration of projects with lower number of stars while less projects will have a large number of stars. For filtering of repositories, we sorted the top 100 projects by the most recently updated. After using a GitHub search API to find projects that met the above criteria, we compiled a list of 789 code repositories. The projects used for our evaluation include a wide range of software applications providing a variety of services. A list of projects used for this study is publicly available online.\footnote{\url{https://gist.github.com/tool-recommender-bot/1769ccd148508beabcd273a731723860}}
%TODO: Maybe examples of projects?

@@

Johnson and colleagues discovered one of the primary barriers to static analysis tool usage among software engineers is false positives in the output~\cite{Johnson2013Why}. To prevent unnecessary recommendations from our system, we manually reviewed all instances where \tool~reported a recommendation should be made. After inspecting each repository modification, \tool~determined whether it was an appropriate case to make a recommendation to the developer. If so, we proceeded to post the comment recommending \textsc{Error Prone} on the code change. Otherwise, we noted the instance of a false positive in our approach and did not make a recommendation.

@@

To futher examine the effectiveness of \tool, we compared our approach to sending email recommendations to developers. To study this, we found similar instances of code fixes by GitHub users where our system would recommend a tool and, instead of making the recommendation with \tool~on the pull request or commit, send an email suggesting \textsc{Error Prone} to the developers. The emails also contained the recommendation feedback survey for developers, and we compared results to see how software engineers responded to receiving a recommendation by email vs. on GitHub from \tool.

@@

Effective tool recommendation systems should have ample opportunities to regularly make recommendations to users. To determine how often \tool~automatically recommends \textsc{Error Prone}, we observed the number of recommendation comments made by our tool. Our evaluation lasted for [some period of time], and we calculated the amount of true positive recommendations during that time span to measure the recommendation rate for each GitHub repository used in our study. To calculate the false positive rate, we compared the number of unnecessary instances where our tool proposed a recommendation found by researchers to the total number of instances where a recommendation reported by \tool.

@@

For our second research question, we accumulated responses from developers in our follow-up survey to determine the usefulness of our system. We utilized a five-point Likert scale for participants to rank how knowledgeable they were about the existence of \textsc{Error Prone} before the recommendation and how likely they are to use \textsc{Error Prone} for future development tasks. An optional free response section was provided at the end for respondents to describe explain why or why not they found the recommendation useful. These responses were used to analyze developers' reactions to our automated recommendation. Finally, researchers analyzed and independently coded open-ended responses from participants to further analyze the effectiveness of our system based on developer feedback.

@@

Non-java changes, documentation, errors removed not fixed, error fixed everywhere in code...

@@

Internal\\

An external threat to the validity of our study is that we only observed open source projects, and our results may not generalize to closed source software projects and their developers. To minimize this, we evaluated \tool~on popular GitHub software applications with a wide variety of goals. Additionally, our recommendation system has limited generalizablility due to the fact we currently only assess recommendations for the Error Prone static analysis tool on Java projects that build with Maven.

@@

To improve discovery of software engineering tools, we aim to increase the practicality and convenience of \tool~for researchers to implement our system with their projects. \tool~currently only works for development tools for Java code. This disregards useful programming tools that focus on other languages such as...

Additionally, our system requires projects that build with Maven. This restriction ignores helpful software engineering tools that implement different build systems, for example,...

>>>>

Our evaluation was limited to Java projects since \textsc{Error Prone} only analyzes Java code. To determine if a repository was a Maven project, we automatically checked if a Project Object Model (\textit{pom.xml}) configuration file was located in the home directory. We also checked to make sure that the pom.xml did not already contain the \textsc{Error Prone} plugin. Our approach targets projects that don't use \textsc{Error Prone} to recommend the tool to developers who are less likely to be knowledgeable about the tool. We chose the most starred repositories to study the most popular projects on GitHub. Stars are a social aspect of GitHub where users can indicate favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}.

To get the most popular repositories, we filtered GitHub projects by the amount of stars based on numbers in the Fibonnaci sequence. This allowed us to get a higher concentration of projects with lower number of stars while less projects will have a large number of stars. For filtering of repositories, we sorted the top 100 projects by the most recently updated. After using a GitHub search API to find projects that met the above criteria, we compiled a list of 789 code repositories. The projects used for our evaluation include a wide range of software applications providing a variety of services from large software companies such as Google and Apache to individual developers. A list of projects used for this study is publicly available online.\footnote{\url{https://gist.github.com/tool-recommender-bot/1769ccd148508beabcd273a731723860}}
%TODO: Maybe examples of projects?

@@

Johnson and colleagues discovered one of the primary barriers to static analysis tool usage among software engineers is false positives in the output~\cite{Johnson2013Why}. To prevent unnecessary recommendations from our system, we manually reviewed all instances where \tool~reported a recommendation should be made. After inspecting each repository modification, \tool~determined whether it was an appropriate case to make a recommendation to the developer. If so, we proceeded to post the comment recommending \textsc{Error Prone} on the code change. Otherwise, we noted the instance of a false positive in our approach and did not make a recommendation. In situations where one commit or pull request provided multiple opportunities for a recommendation, the authors would examine the changes and select one of the errors reported as fixed to recommend \textsc{Error Prone} to the developer.

@@

To futher examine the effectiveness of \tool, we compared our approach to sending email recommendations to developers. To study this, we found similar instances of code fixes by GitHub users where our system would recommend a tool and, instead of making the recommendation with \tool~on the pull request or commit, send an email suggesting \textsc{Error Prone} to the developers. The emails also contained the recommendation feedback survey for developers, and we compared results to see how software engineers responded to receiving a recommendation by email vs. on GitHub from \tool. To send a recommendation via email, the developer must have an email address publicly available on the GitHub user profile.

@@

Effective tool recommendation systems should have ample opportunities to regularly make recommendations to users. To determine how often \tool~automatically recommends \textsc{Error Prone}, we observed the total number of new pull requests and commits, and compared it to the amount recommendations made by our tool. We calculated the rate of true positive recommendations during the span of our study to measure the recommendation rate for each GitHub repository used in our evaluation. To calculate the false positive rate, we compared the number of unnecessary instances where our tool proposed a recommendation found by researchers to the total number of instances where a recommendation reported by \tool.

@@

For our second research question, we accumulated responses from developers in our follow-up survey presented in recommendations from \tool~and by email to determine the usefulness of our system. We utilized a five-point Likert scale for participants to rank how knowledgeable they were about the existence of \textsc{Error Prone} before the recommendation and how likely they are to use \textsc{Error Prone} for future development tasks. An optional free response section was provided at the end for respondents to describe explain why or why not they found the recommendation useful. These responses were used to analyze developers' reactions to our automated recommendation. Finally, researchers analyzed and independently coded open-ended responses from participants to further analyze the effectiveness of our approach based on feedback from software developers.

@@

Non-java changes, number of errors removed but not fixed, number of errors fixed without another instance in the code, manual inspection of pull requests and commits...

@@

An internal threat to the validity of this work is our use of code differencing to determine if developers intended to fix a bug in a commit or pull request. We cannot definitively determine the intentions of GitHub developers making changes to a repository, however two authors analyzed the code changes and came to an agreement on if the modified patch was a fix before making a recommendation to the developer. Additionally, although we used a Likert scale to measure if GitHub users who received a recommendation were likely to use \textsc{Error Prone} in the future, we did not measure if the tool was actually adopted by the developers for future tasks.

Our evaluation has limited generalizablility due to the fact we only assessed recommendations for the \textsc{Error Prone} static analysis tool. This restricted our study to evaluate Java projects and a specific set of errors that can be reported by the tool. We selected \textsc{Error Prone} because it is able to report a wide variety of errors based on bug patterns for Java code. Another external threat to the validity of this study is the projects selected for our evaluation. We only examined open source repositories on GitHub, and these results may not generalize to developers of closed source software or projects on other code hosting sites, such as BitBucket.\footnote{http://bitbucket.org} To minimize this threat, we evaluated \tool~on a large number of popular software applications on GitHub that provide many different services from a wide variety of software companies and developers.

@@

To improve discovery of software engineering tools, we plan to increase the practicality of \tool~for researchers to implement our system with their projects. A next step is to extend our approach to work with multiple static analysis tools, such as Checkstyle\footnote{http://checkstyle.sourceforge.net/} for Java. This will allow us to have more opportunities to make recommendations to developers based on the output from different tools. Additionally, we plan to update our system to work with software engineering tools that integrate as plugins for different build systems such as Gradle\footnote{https://gradle.org/} and Travis CI\footnote{https://travis-ci.org/}, as opposed to just Maven projects. Future work will also extend \tool~to work with different types of tools to increase adoption and usage, for example Find Security Bugs\footnote{https://find-sec-bugs.github.io/} which is useful for finding security vulnerabilities in Java web applications. Finally, future work will consist of expanding \tool~to work with software engineering tools for different programming languages, such as the Pylint\footnote{https://www.pylint.org/} static analysis tool for Python, clang\footnote{https://clang.llvm.org/} compiler and static analyzer for C and C++, and more.
